### 2012-03-31 doc/theses/mikula/diplomka.tex
Master thesis: In progress.
Master thesis: Corrections.

Název práce:
\mftitle
% přesně dle zadání

@@

Katedra:  % Případně Ústav:
Název katedry či ústavu, kde byla práce oficiálně zadána
% dle Organizační struktury MFF UK

Vedoucí diplomové práce:
\mfadvisor, pracoviště
% dle Organizační struktury MFF UK, případně plný název pracoviątě mimo MFF UK

Abstrakt:
% abstrakt v rozsahu 80-200 slov; nejedná se vąak o opis zadání diplomové práce

Klíčová slova:
% 3 aľ 5 klíčových slov

@@

Department:
Název katedry či ústavu, kde byla práce oficiálně zadána
% dle Organizační struktury MFF UK v angličtině

Supervisor:
\mfadvisor, pracoviště
% dle Organizační struktury MFF UK, případně plný název pracoviątě
% mimo MFF UK v angličtině

Abstract:
% abstrakt v rozsahu 80-200 slov v angličtině; nejedná se vąak o překlad
% zadání diplomové práce

Keywords:
% 3 aľ 5 klíčových slov v angličtině

@@

%%% Tabulky v diplomové práci, existují-li.
%\chapwithtoc{List of Tables}
\listoftables
\todo[inline]{Je List of Tables potrebny? Co figures?}

>>>>

Název práce:
Odvozování XML schémy se znalostí XML operací
% přesně dle zadání

@@

Katedra:  % Případně Ústav:
Katedra softwarového inženýrství
% dle Organizační struktury MFF UK

Vedoucí diplomové práce:
\mfadvisor
% dle Organizační struktury MFF UK, případně plný název pracoviątě mimo MFF UK

Abstrakt: \todo[inline]{TODO cca 10-15 riadkov}
% abstrakt v rozsahu 80-200 slov; nejedná se vąak o opis zadání diplomové práce

Klíčová slova: \todo[inline]{TODO 5-8 slov}
% 3 aľ 5 klíčových slov

@@

Department:
Department of Software Engineering
% dle Organizační struktury MFF UK v angličtině

Supervisor:
\mfadvisor
% dle Organizační struktury MFF UK, případně plný název pracoviątě
% mimo MFF UK v angličtině

Abstract: \todo[inline]{TODO}
% abstrakt v rozsahu 80-200 slov v angličtině; nejedná se vąak o překlad
% zadání diplomové práce

Keywords: \todo[inline]{TODO}
% 3 aľ 5 klíčových slov v angličtině

@@

%%% Tabulky v diplomové práci, existují-li.
%\chapwithtoc{List of Tables}
\listoftables

### 2012-03-31 doc/theses/mikula/proposed_algorithm.tex
Master thesis: Corrections.

\section{Motivation}
There is a large space of possible XQuery utilizations, but obviously, they all cannot be covered by one thesis. Hence, we had to choose only some of them. We decided to focus on an inference of XSD built-in atomic types of elements and attributes, and a key discovery.

@@

As a second part of the algorithm, we decided to extend the only method \cite{Necasky:2009:DXK:1529282.1529414} which utilizes XQuery queries and infers keys and foreign keys. The extension is based on a more general and precise processing of queries, addition of a new case of query patterns that are used in the process, and a more accurate summary of key statements by incorporating a search for statements that reject a uniqueness of certain elements and attributes.

@@

\subsection{Normalization of Key Statements}
The original approach \cite{Necasky:2009:DXK:1529282.1529414} employs the following normalization which we adopt. Is also incorporates a heuristic for precision enhancement. For details, refer to it.

>>>>

\section{Motivation}
There is a large space of possible XQuery utilizations, but obviously, they all cannot be covered by one thesis. Hence, we had to choose only some of them. We decided to focus on inference of XSD built-in atomic types of elements and attributes, and key discovery.

@@

As a second part of the algorithm, we decided to extend the only method \cite{Necasky:2009:DXK:1529282.1529414} which utilizes XQuery queries and infers keys and foreign keys. The extension is based on a more general and precise processing of queries, addition of a new case of query patterns that are used in the process, and a more accurate summary of key statements by incorporating searching for statements that reject uniqueness of certain elements and attributes.

@@

\subsection{Normalization of Key Statements}
The original approach \cite{Necasky:2009:DXK:1529282.1529414} employs the following normalization which we adopt. Is also incorporates a heuristic for precision enhancement. For details, we refer to it.

### 2012-03-31 doc/theses/mikula/used_technologies_and_definitions.tex
Master thesis: Corrections.

\subsection{Usage Examples}
Finally, we introduce several examples of XPath expressions, with their description, using the sample XML in Figure \ref{FIG_a_simple_xml_example}.

>>>>

\subsection{Usage Examples}
Finally, we introduce several examples of XPath expressions, with their description, using the sample XML document in Figure \ref{FIG_a_simple_xml_example}.
